Variable Selection

### 2015-06-19 var_select.rmd
added cforest

```{r, echo=FALSE, include=FALSE}
library('knitr')
# library('knitr', lib = 'C:/Progra~1/R/R-3.1.2/library')
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.1.3/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.1.3/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.0/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.0/library')

library('ggplot2')
library("dplyr")
library("plyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
```

@@

>>>>

```{r, echo=FALSE, include=FALSE}
# library('knitr')
library('knitr', lib = 'C:/Progra~1/R/R-3.1.2/library')
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
library('ggplot2', lib = 'C:/Progra~1/R/R-3.1.2/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
library('magrittr',lib='C:/Progra~1/R/R-3.1.3/library')
library('reshape2',lib='C:/Progra~1/R/R-3.1.3/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.0/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.0/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.0/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.0/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.0/library')

# library('ggplot2')
# library("dplyr")
# library("plyr")
# library('magrittr')
# library('reshape2')
# library("rpart")
# library('car')
# library('e1071')
# library('corrgram')
# library('party')
```

@@

Use cforest from party package - (Strobl etc, 2007)
- must be subsampling without replacement
- subsampling size 0.632 times recommended because about 63.2% of data end up in bootstrap sample

all7b<- all7a %>% select(return.pdol, no.users,timespan,mean.peeps,hours.perday,Num.disc,pc.pro,
                num.inv, pc.gradpro , inv.mlsto , client.numinv, client.totinv, client.meaninv , 
                client.neginv , mean.inv , pc.director , code.client , Post.Code , Billing.Type , 
                Discipline , Job.Detail.Primary , Job.Detail.Secondary , Job.Type.Primary , 
                Job.Type.Secondary , State , Type , Business , Biz.size , Biz.type , JD.Primary ,
                JD.Second , code.director , code.ProjEng , ProjEng.Pos , code.Eng2 , Eng2.Pos)

var.imp<- cforest(return.pdol~.,
        data= all7b
        )
